\documentclass[journal]{IEEEtran}

% packages
\usepackage{lipsum}
\usepackage{ulem}
\usepackage{hyperref}
% \usepackage{flushend}
\usepackage[inline]{enumitem}
\usepackage{array,multirow,graphicx}
\usepackage{float}
\usepackage{orcidlink}

%% footnote
\usepackage{footnote}
\makesavenoteenv{tabular}
\makesavenoteenv{table}
\makesavenoteenv{tabular*}
\makesavenoteenv{table*}
% \usepackage{tablefootnote}

%% graphics packages
\usepackage{tikz}
\usepackage{colortbl}
\usepackage{pgfplots}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{circuitikz}
\usepackage{dblfloatfix}
\usepackage[bottom]{footmisc}
\ifCLASSOPTIONcompsoc
    \usepackage[caption=false, font=normalsize, labelfont=sf, textfont=sf]{subfig}
\else
    \usepackage[caption=false, font=footnotesize]{subfig}
\fi

%% checkmark packages 
\usepackage{pifont}
\newcommand{\cmark}{\ding{51}}
\newcommand{\xmark}{\ding{55}}

%% math packages
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{booktabs}

% math 
\IEEEeqnarraydefcolsep{0}{\hoffset}
\newcommand*{\defeq}{\stackrel{\text{def}}{=}}

% definition setup
%\theoremstyle{definition}

\newtheorem{defn}{Definition}[section]

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

% nomenclature
\input{nomenclature}

% document
\begin{document}

% title, authors and thanks
\title{Robust Lower Bound for \\ Equitable Harmonic Hosting Capacity}
\author{Tom~Van~Acker~\orcidlink{0000-0001-6283-1457},%
        Benoit~Legat~\orcidlink{?}, %
        Hatice~Calik~\orcidlink{0000-0002-9972-6199}, %
        and~Hakan~Ergun,~\IEEEmembership{Senior Member,~IEEE}~\orcidlink{0000-0001-5171-1986}%
\thanks{Tom Van Acker is with the Department of Technology Expertise Power, BASF Antwerp, 2000 Antwerp, Belgium (e-mail: tom.a.van-acker@basf.com).}% <-this % stops a space
\thanks{Benoit Legat is with the Research Group ICTEAM, Department of Mathematical Engineering, UCLouvain, 1348 Louvain-la-Neuve, Belgium (e-mail: benoit.legat@uclouvain.be)}% <- this % stops a space
\thanks{Hatice Calik and Hakan Ergun are with the Research Group ELECTA, Department of Electrical Engineering, KU Leuven, 3000 Leuven, Belgium, and also with Etch-EnergyVille, 3600 Genk, Belgium (e-mail: hatice.calik@kuleuven.be, hakan.ergun@kuleuven.be).}
\thanks{This work is supported by the Energy Transition Fund by FOD Economy, Belgium, project HARMONIC. The General Board on Energy of the FOD Economy is not liable for any use of the presented work and subsequent results.}
\thanks{\textit{(Corresponding author: Tom~Van~Acker)}}}

% paper headers
\markboth{Journal of \LaTeX\ Class Files,~Vol.~14, No.~8, August~2015}%
{Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for IEEE Journals}

% make the title area
\maketitle

% abstract
\begin{abstract}
\end{abstract}

% keywords
\begin{IEEEkeywords}
Harmonic distortion, robust, fairness, hosting capacity, mathematical optimization.
\end{IEEEkeywords}

% peer-review title
\IEEEpeerreviewmaketitle

\input{journals/rhhcp/sections/introduction}

\newpage
~
\newpage

\input{journals/rhhcp/sections/mathematical_framework}

\newpage

\input{journals/rhhcp/sections/numerical_illustration}
\input{journals/rhhcp/sections/conclusion}

\newpage
~
\newpage

% appendices
\input{journals/rhhcp/appendix/appendix_model}

% bibliography
\bibliographystyle{IEEEtran}
% \bibliography{journals/rhhc/harmonic_references}

% biographies
\begin{IEEEbiographynophoto}{Dr. Ir. Ing. Tom Van Acker} received the M.Eng., M.Sc. and Ph.D. degrees in Electrical Engineering from KU Leuven, Leuven, Belgium in 2012, 2014 and 2020, respectively. Currently, he is a Power System Expert at BASF Antwerp. His main areas of research interest are optimization and uncertainty in a power system context, specifically applied in the context of availability, harmonics, optimal power flow, and state estimation. 
\end{IEEEbiographynophoto}

\begin{IEEEbiographynophoto}{Dr. Benoit Legat} received the Ph.D. degree in Applied Mathematics from the UCLouvain, Louvain-la-Neuve, Belgium, in 2020. Currently, he is an Assistant Professor with UCLouvain. His research interests include global landscape analysis of non-convex optimization problems as well as their convex formulations with a focus on the fields of machine learning, polynomial optimization, invariant-set computation and optimal control.
\end{IEEEbiographynophoto}

\begin{IEEEbiographynophoto}{Dr. Dipl.-Ing. Hakan Ergun} received his Ph.D. degree in Electrical Engineering for KU Leuven, Belgium in 2015. Currently, he is an Associate Professor with KU Leuven and the Energy Transmission Competence Hub (Etch) within EnergyVille. His research interest is to optimally develop and operate future energy networks for the renewable energy transition. He is the main developer of a number of open-source network modelling tools for optimal planning and operation of AC and DC grids, and stability and security constrained network operation.
\end{IEEEbiographynophoto}

\end{document}
