\section{Initial Validation Steps}

Necessary steps:
\begin{enumerate}
    \item validation of tractability of second order cone problems with simple interval uncertainty.
\end{enumerate}

Nice to have steps:
\begin{enumerate}
    \item find tractable harmonic unit model; and
    \item find a number of metrics to model 'fair' distribution of hosting capacity amongst units.
\end{enumerate}

\section{Introduction}
\label{sec:introduction}

\subsection{Background and Motivation}
\label{sec:background_and_motivation}

The underlying decision environment of robust optimization has the following characteristics:
\begin{enumerate}
    \item all decision variables represent "here-and-now" decisions;
    \item the consequences of the decisions are valid when, and only when, the actual data is within the prespecified uncertainty set; and
    \item the constraints are hard, i.e., no violation of constrains is tolerated.
\end{enumerate}

The robust optimal solution is simply "the best uncertainty-immunized" solution. The considered uncertainties are:
\begin{enumerate}
    \item edge impedances:~$\SeriesReactance{\Line,\Harmonic}$, $\SeriesResistance{\Line,\Harmonic}$, $\ShuntConductance{\LineTuple,\Harmonic}$ and $\ShuntSusceptance{\LineTuple,\Harmonic}$,
    \item fundamental voltage magnitude, and
    \item infinite source voltage.
\end{enumerate}

A distinction is made between two types of uncertainty:
\begin{enumerate}
    \item set inclusion uncertainty, i.e., where the uncertain parameters are only known to belong to some bounded uncertainty set, and
    \item probabilistic uncertainty, i.e., where the uncertain parameters are random vectors belong to some set of probability distribution functions.
\end{enumerate}

% \IEEEPARstart{T}{HE}

\subsection{Literature Review}
\label{sec:literature_review}

\begin{enumerate}
    \item Considerations on hosting capacity for harmonic distortions on transmission and distribution systems, I.N.~Santos et al.
    \item Harmonic Optimal Power Flow with Transformer Excitation, F.~Geth et al. 
    \item Robust Power Flow and Three-Phase Power Flow Analyses, A.~Pandey et al.
    \item A Guide to Formulating Equity and Fairness in an Optimization Model, Hooker et al.
\end{enumerate}

\subsection{Contributions and Outline}
\label{sec:contributions_and_outline}

\newpage